Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2019-02-13 hpmoon-asoco.tex
Rearranges figures to make them embedded in text

Different metrics, previously explained, have been used
to calculate the quality of the obtained PFs in each configuration. As HV \textcolor{blue}{requires} a reference point to be
calculated (see Figure \ref{fig:hypervolume}), we have chosen the value (1,9) as none of the existing solutions on all fronts obtained during all executions are dominated by it. In other words, as we are minimizing in both objectives, this reference point is required to be numerically larger or equal in each objective, and strictly larger in at least one of them (dominated) for all solutions in the PFs we are going to measure. HV is then
normalized \textcolor{blue}{with respect to} to that point. Also, the optimal reference PF distribution used to calculate the IGD and Spread metrics \cite{Durillo11Jmetal} has 1000 solutions \footnote{Optimal PFs are available at:   \url{http://www.tik.ee.ethz.ch/sop/download/supplementary/testproblems/}.} .  
A Kruskal-Wallis significance
test has been performed to the metrics of all runs of the
configurations, as the Kolmogorov-Smirnov test detected non-normal
distributions. The average results for each configuration are shown in
Table \ref{tab:results512} (for 512 dimensions) and Table
\ref{tab:results2048} (for 2048). As previously explained, when $P=8$
the results of A are equivalent to the obtained by D (because
$c=0$), and when $P=16$ they are equivalent to O ($c=1$). We refer this equivalence with the word {\em Equiv-} in tables. For example, Equiv-D in an HV cell  means that the HV of A is the same than the value in D column, because the behaviour of this configuration is the same than executing D.

@@

@@

\begin{table*}
\centering
\resizebox{12cm}{!}{
\begin{tabular}{|c||c|c|c|c||c|c|c|c||}
\hline
	&	\multicolumn{4}{|c|}{Average solutions per front}													&	\multicolumn{4}{|c|}{Generations}															\\ \hline

\#Island	&	B		&	D		&	O			&	A			&	B		&	D			&	O			&	A				\\ \hline
\multicolumn{9}{|c|}{ZDT1}																				\\ \hline
8	&	182.700		&	128.500		&	158.167			&	Equiv-D			&	397.367		&	776.967			&	603.667			&	Equiv-D				\\
16	&	132.567		&	43.633		&	76.167			&	Equiv-O			&	567.933		&	908.467			&	838.000			&	Equiv-O				\\
32	&	102.200		&	37.533		&	34.133	D		&	52.033			&	731.067		&	959.067			&	938.167			&	917.000				\\
64	&	81.100		&	46.267		&	26.300			&	30.167		O	&	846.733		&	978.733			&	972.567			&	927.133	B			\\
128	&	77.167		&	57.767		&	35.767			&	29.167		O	&	923.133		&	984.767			&	984.233	D		&	967.933				\\ \hline
\multicolumn{9}{|c|}{ZDT2}																															\\ \hline
8	&	122.700		&	91.633		&	108.833	BD		&	Equiv-D			&	398.167		&	772.000			&	605.100			&	Equiv-D				\\
16	&	94.867		&	28.033		&	62.467			&	Equiv-O			&	574.567		&	908.433			&	840.900			&	Equiv-O				\\
32	&	56.633		&	11.433		&	19.467	D		&	31.567			&	735.867		&	960.167			&	939.200			&	904.900				\\
64	&	33.467		&	10.267		&	9.367	D		&	19.067			&	849.900		&	978.600			&	972.167			&	929.800	B			\\
128	&	22.833		&	12.633		&	7.800			&	13.967		D	&	929.433		&	984.567			&	984.233	D		&	971.700				\\ \hline
\multicolumn{9}{|c|}{ZDT3}																															\\ \hline
8	&	212.900		&	129.233		&	171.367			&	Equiv-D			&	398.633		&	776.000			&	603.333			&	Equiv-D				\\
16	&	176.133		&	43.567		&	90.100			&	Equiv-O			&	573.033		&	908.667			&	838.000			&	Equiv-O				\\
32	&	121.500		&	42.800		&	33.200			&	56.900			&	733.233		&	959.000			&	937.967			&	918.833				\\
64	&	96.500		&	54.267		&	34.900			&	37.800		O	&	849.200		&	977.167			&	972.200			&	933.167				\\
128	&	76.700		&	62.200		&	41.767			&	33.867		D	&	924.000		&	984.733			&	984.367	D		&	966.433				\\ \hline
\multicolumn{9}{|c|}{ZDT6}																															\\ \hline
8	&	42.233		&	28.633		&	35.967	BD		&	Equiv-D			&	396.900		&	773.400			&	603.533			&	Equiv-D				\\
16	&	43.733		&	7.733		&	18.967			&	Equiv-O			&	568.200		&	908.900			&	836.033			&	Equiv-O				\\
32	&	35.533		&	8.033		&	8.633	D		&	16.233		DO	&	735.700		&	958.900			&	938.600			&	926.167				\\
64	&	22.600		&	10.700		&	7.500	D		&	7.533		DO	&	850.267		&	978.067			&	972.467			&	940.267				\\
128	&	18.133		&	15.000	B	&	9.067			&	11.367		D	&	927.233		&	984.667			&	983.933	D		&	969.433				\\ \hline
\end{tabular}
}
\caption{Average number of generations and average number of solutions of the front, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and \textcolor{blue}{automatic} overlapped (A), using a chromosome length of 512 dimensions. Acronyms next to values indicate that there is not significant difference with respect to that method for that value. Equiv-$X$ implies that value is the same as executing $X$, since both configurations would be the same.}
\label{tab:sols512}
\end{table*}

\begin{table*}
\centering
\resizebox{12cm}{!}{
\begin{tabular}{|c||c|c|c|c||c|c|c|c||}
\hline
	&	\multicolumn{4}{|c|}{Average solutions per front}													&	\multicolumn{4}{|c|}{Generations}															\\ \hline
%\multicolumn{13}{|c|}{2048 dimensions}																															\\ \hline
\#Island	&	B		&	D		&	O			&	A			&	B		&	D			&	O			&	A				\\ \hline
\multicolumn{9}{|c|}{ZDT1}																					\\ \hline
8	&	137.733		&	47.167		&	119.933	B		&	Equiv-D			&	175.067		&	225.667			&	207.933			&	Equiv-D				\\
16	&	92.633		&	38.233		&	47.533	D		&	Equiv-O			&	204.867		&	238.533			&	232.900			&	Equiv-O				\\
32	&	56.167		&	41.167		&	28.667			&	32.567	O		&	225.433		&	243.833			&	242.533			&	242.000	O			\\
64	&	50.900		&	49.667	B	&	35.600			&	25.367			&	236.500		&	245.967			&	245.700			&	244.033	D			\\
128	&	45.767		&	64.933		&	44.167	B		&	31.867			&	242.800		&	247.000			&	247.000	D		&	245.733				\\ \hline
\multicolumn{9}{|c|}{ZDT2}																															\\ \hline
8	&	64.267		&	22.733		&	56.867	B		&	Equiv-D			&	175.633		&	226.000			&	208.100			&	Equiv-D				\\
16	&	52.300		&	10.733		&	20.067	D		&	Equiv-O			&	205.033		&	238.867			&	233.100			&	Equiv-O				\\
32	&	34.400		&	10.367		&	10.433	D		&	17.900	O		&	225.600		&	244.267			&	242.633			&	242.000	O			\\
64	&	24.600		&	10.900		&	9.267	D		&	12.867	DO		&	236.700		&	246.000			&	245.767			&	244.033	D			\\
128	&	18.667		&	17.833	B	&	10.367			&	12.933	O		&	243.367		&	247.000			&	247.000	d		&	245.833				\\ \hline
\multicolumn{9}{|c|}{ZDT3}																															\\ \hline
8	&	163.767		&	83.367		&	119.467			&	Equiv-D			&	176.533		&	226.400			&	207.700			&	Equiv-D				\\
16	&	108.467		&	49.433		&	47.700	D		&	Equiv-O			&	205.333		&	238.467			&	232.933			&	Equiv-O				\\
32	&	72.133		&	44.333		&	31.833			&	36.533	O		&	225.100		&	243.900			&	242.433			&	242.000	O			\\
64	&	54.867		&	57.600	B	&	40.633			&	29.300			&	236.333		&	245.933			&	245.733			&	244.000	D			\\
128	&	50.600		&	72.133		&	49.033	B		&	34.933			&	243.200		&	247.000			&	247.000	D		&	245.833				\\ \hline
\multicolumn{9}{|c|}{ZDT6}																															\\ \hline
8	&	22.133		&	13.833		&	14.433	D		&	Equiv-D			&	175.733		&	226.100			&	207.767			&	Equiv-D				\\
16	&	20.767		&	15.867		&	13.300	D		&	Equiv-O			&	205.033		&	238.433			&	232.933			&	Equiv-O				\\
32	&	22.600		&	10.700		&	10.033	D		&	11.967	DO		&	225.833		&	243.667			&	242.500			&	242.000	O			\\
64	&	19.033		&	11.267		&	10.533	D		&	10.567	DO		&	236.433		&	245.900			&	245.833			&	244.000	D			\\
128	&	15.800		&	24.500		&	11.600			&	12.233	DO		&	243.800		&	247.000			&	247.000	D		&	245.533				\\ \hline
\end{tabular}
}
\caption{Average number of generations and average number of solutions per front, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and \textcolor{blue}{automatic} overlapped (A), using a chromosome length of 2048 dimensions. Acronyms next to values indicate that there is not significant difference with respect to that method for that value. Equiv-$X$ implies that value is the same as executing $X$, since both configurations would be the same.}
\label{tab:sols2048}
\end{table*}

@@

%ZDT1
\begin{figure}
\centering
\includegraphics[width=12cm]{plot_zdt1_512.png}
\caption{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }
\label{fig:plot_zdt1_512}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=12cm]{plot_zdt1_2048.png}
\caption{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }
\label{fig:plot_zdt1_2048}
\end{figure}

%ZDT2
\begin{figure}
\centering
\includegraphics[width=12cm]{plot_zdt2_512.png}
\caption{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }
\label{fig:plot_zdt2_512}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=12cm]{plot_zdt2_2048.png}
\caption{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }
\label{fig:plot_zdt2_2048}
\end{figure}

%ZDT3
\begin{figure}
\centering
\includegraphics[width=12cm]{plot_zdt3_512.png}
\caption{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }
\label{fig:plot_zdt3_512}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=12cm]{plot_zdt3_2048.png}
\caption{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }
\label{fig:plot_zdt3_2048}
\end{figure}

%ZDT6
\begin{figure}
\centering
\includegraphics[width=12cm]{plot_zdt6_512.png}
\caption{PFs obtained in one arbitrary run for the ZDT6 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }
\label{fig:plot_zdt6_512}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=12cm]{plot_zdt6_2048.png}
\caption{PFs obtained in one arbitrary run for the ZDT6 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }
\label{fig:plot_zdt6_2048}
\end{figure}

%EXPLANATION OF THE RESULTS
This can be explained comparing the number of non-dominated solutions
of each front and the average number of generations (Table
\ref{tab:sols512} and Table \ref{tab:sols2048}). With both chromosome
lengths, increasing the number of islands implies more generations
with all the methods (logically, as there are \textcolor{blue}{fewer} individuals in each
island). But also, the SLA methods
approach to the number of generations with the baseline when
increasing the number of islands. However, with $L=2048$ the migration
time is big enough  to not improve the number of generations
with respect to the baseline, even in the lower number of islands, as
it happens with $L=512$. Therefore, more generations do not
necessarily mean improve the solution of the global PF, but focusing on
different elements of the chromosome. As  previously stated, every
island is unaware of the other islands PFs, and they are trying to
optimize their solutions independently. With respect to the average
number of solutions per front, there is a clear difference 
 with the baseline with $L=512$, where this value is in the most
of the cases, less than a half. The number of non-dominated solutions
also implies a better Spread indicator, where the baseline 
 obtains better (or not significantly different) values in the majority of the compared configurations.

>>>>

Different metrics, previously explained, have been used
to calculate the quality of the obtained PFs in every configuration. As HV \textcolor{blue}{requires} a reference point to be
calculated (see Figure \ref{fig:hypervolume}), we have chosen the value (1,9) as none of the existing solutions on all fronts obtained during all executions are dominated by it. In other words, as we are minimizing in both objectives, this reference point is required to be numerically larger or equal in each objective, and strictly larger in at least one of them (dominated) for all solutions in the PFs we are going to measure. HV is then
normalized \textcolor{blue}{with respect to} to that point. Also, the optimal reference PF distribution used to calculate the IGD and Spread metrics \cite{Durillo11Jmetal} has 1000 solutions \footnote{Optimal PFs are available at:   \url{http://www.tik.ee.ethz.ch/sop/download/supplementary/testproblems/}.} .  
A Kruskal-Wallis significance
test has been performed to the metrics of all runs of the
configurations, as the Kolmogorov-Smirnov test detected non-normal
distributions.
%

@@

The average results for each configuration are shown in
Table \ref{tab:results512} (for 512 dimensions) and Table
\ref{tab:results2048} (for 2048). As previously explained, when $P=8$
the results of A are equivalent to the obtained by D (because
$c=0$), and when $P=16$ they are equivalent to O ($c=1$). We refer this equivalence with the word {\em Equiv-} in tables. For example, Equiv-D in an HV cell  means that the HV of A is the same than the value in D column, because the behaviour of this configuration is the same than executing D.

@@

@@

\begin{table*}[h!tb]
\centering
\resizebox{12cm}{!}{
\begin{tabular}{|c||c|c|c|c||c|c|c|c||}
\hline
	&	\multicolumn{4}{|c|}{Average solutions per front}													&	\multicolumn{4}{|c|}{Generations}															\\ \hline

\#Island	&	B		&	D		&	O			&	A			&	B		&	D			&	O			&	A				\\ \hline
\multicolumn{9}{|c|}{ZDT1}																				\\ \hline
8	&	182.700		&	128.500		&	158.167			&	Equiv-D			&	397.367		&	776.967			&	603.667			&	Equiv-D				\\
16	&	132.567		&	43.633		&	76.167			&	Equiv-O			&	567.933		&	908.467			&	838.000			&	Equiv-O				\\
32	&	102.200		&	37.533		&	34.133	D		&	52.033			&	731.067		&	959.067			&	938.167			&	917.000				\\
64	&	81.100		&	46.267		&	26.300			&	30.167		O	&	846.733		&	978.733			&	972.567			&	927.133	B			\\
128	&	77.167		&	57.767		&	35.767			&	29.167		O	&	923.133		&	984.767			&	984.233	D		&	967.933				\\ \hline
\multicolumn{9}{|c|}{ZDT2}																															\\ \hline
8	&	122.700		&	91.633		&	108.833	BD		&	Equiv-D			&	398.167		&	772.000			&	605.100			&	Equiv-D				\\
16	&	94.867		&	28.033		&	62.467			&	Equiv-O			&	574.567		&	908.433			&	840.900			&	Equiv-O				\\
32	&	56.633		&	11.433		&	19.467	D		&	31.567			&	735.867		&	960.167			&	939.200			&	904.900				\\
64	&	33.467		&	10.267		&	9.367	D		&	19.067			&	849.900		&	978.600			&	972.167			&	929.800	B			\\
128	&	22.833		&	12.633		&	7.800			&	13.967		D	&	929.433		&	984.567			&	984.233	D		&	971.700				\\ \hline
\multicolumn{9}{|c|}{ZDT3}																															\\ \hline
8	&	212.900		&	129.233		&	171.367			&	Equiv-D			&	398.633		&	776.000			&	603.333			&	Equiv-D				\\
16	&	176.133		&	43.567		&	90.100			&	Equiv-O			&	573.033		&	908.667			&	838.000			&	Equiv-O				\\
32	&	121.500		&	42.800		&	33.200			&	56.900			&	733.233		&	959.000			&	937.967			&	918.833				\\
64	&	96.500		&	54.267		&	34.900			&	37.800		O	&	849.200		&	977.167			&	972.200			&	933.167				\\
128	&	76.700		&	62.200		&	41.767			&	33.867		D	&	924.000		&	984.733			&	984.367	D		&	966.433				\\ \hline
\multicolumn{9}{|c|}{ZDT6}																															\\ \hline
8	&	42.233		&	28.633		&	35.967	BD		&	Equiv-D			&	396.900		&	773.400			&	603.533			&	Equiv-D				\\
16	&	43.733		&	7.733		&	18.967			&	Equiv-O			&	568.200		&	908.900			&	836.033			&	Equiv-O				\\
32	&	35.533		&	8.033		&	8.633	D		&	16.233		DO	&	735.700		&	958.900			&	938.600			&	926.167				\\
64	&	22.600		&	10.700		&	7.500	D		&	7.533		DO	&	850.267		&	978.067			&	972.467			&	940.267				\\
128	&	18.133		&	15.000	B	&	9.067			&	11.367		D	&	927.233		&	984.667			&	983.933	D		&	969.433				\\ \hline
\end{tabular}
}
\caption{Average number of generations and  solutions per front, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and \textcolor{blue}{automatic} overlapped (A), using a chromosome length of 512 dimensions. Acronyms next to values indicate that there is not significant difference with respect to that method for that value. Equiv-$X$ implies that value is the same as executing $X$, since both configurations would be the same.}
\label{tab:sols512}
\end{table*}
%
\begin{table*}[h!tb]
\resizebox{12cm}{!}{
\begin{tabular}{|c||c|c|c|c||c|c|c|c||}
	&	\multicolumn{4}{|c|}{Average solutions per front}													&	\multicolumn{4}{|c|}{Generations}															\\ \hline
%\multicolumn{13}{|c|}{2048 dimensions}																															\\ \hline
\#Island	&	B		&	D		&	O			&	A			&	B		&	D			&	O			&	A				\\ \hline
\multicolumn{9}{|c|}{ZDT1}																					\\ \hline
8	&	137.733		&	47.167		&	119.933	B		&	Equiv-D			&	175.067		&	225.667			&	207.933			&	Equiv-D				\\
16	&	92.633		&	38.233		&	47.533	D		&	Equiv-O			&	204.867		&	238.533			&	232.900			&	Equiv-O				\\
32	&	56.167		&	41.167		&	28.667			&	32.567	O		&	225.433		&	243.833			&	242.533			&	242.000	O			\\
64	&	50.900		&	49.667	B	&	35.600			&	25.367			&	236.500		&	245.967			&	245.700			&	244.033	D			\\
128	&	45.767		&	64.933		&	44.167	B		&	31.867			&	242.800		&	247.000			&	247.000	D		&	245.733				\\ \hline
\multicolumn{9}{|c|}{ZDT2}																															\\ \hline
8	&	64.267		&	22.733		&	56.867	B		&	Equiv-D			&	175.633		&	226.000			&	208.100			&	Equiv-D				\\
16	&	52.300		&	10.733		&	20.067	D		&	Equiv-O			&	205.033		&	238.867			&	233.100			&	Equiv-O				\\
32	&	34.400		&	10.367		&	10.433	D		&	17.900	O		&	225.600		&	244.267			&	242.633			&	242.000	O			\\
64	&	24.600		&	10.900		&	9.267	D		&	12.867	DO		&	236.700		&	246.000			&	245.767			&	244.033	D			\\
128	&	18.667		&	17.833	B	&	10.367			&	12.933	O		&	243.367		&	247.000			&	247.000	d		&	245.833				\\ \hline
\multicolumn{9}{|c|}{ZDT3}																															\\ \hline
8	&	163.767		&	83.367		&	119.467			&	Equiv-D			&	176.533		&	226.400			&	207.700			&	Equiv-D				\\
16	&	108.467		&	49.433		&	47.700	D		&	Equiv-O			&	205.333		&	238.467			&	232.933			&	Equiv-O				\\
32	&	72.133		&	44.333		&	31.833			&	36.533	O		&	225.100		&	243.900			&	242.433			&	242.000	O			\\
64	&	54.867		&	57.600	B	&	40.633			&	29.300			&	236.333		&	245.933			&	245.733			&	244.000	D			\\
128	&	50.600		&	72.133		&	49.033	B		&	34.933			&	243.200		&	247.000			&	247.000	D		&	245.833				\\ \hline
\multicolumn{9}{|c|}{ZDT6}																															\\ \hline
8	&	22.133		&	13.833		&	14.433	D		&	Equiv-D			&	175.733		&	226.100			&	207.767			&	Equiv-D				\\
16	&	20.767		&	15.867		&	13.300	D		&	Equiv-O			&	205.033		&	238.433			&	232.933			&	Equiv-O				\\
32	&	22.600		&	10.700		&	10.033	D		&	11.967	DO		&	225.833		&	243.667			&	242.500			&	242.000	O			\\
64	&	19.033		&	11.267		&	10.533	D		&	10.567	DO		&	236.433		&	245.900			&	245.833			&	244.000	D			\\
128	&	15.800		&	24.500		&	11.600			&	12.233	DO		&	243.800		&	247.000			&	247.000	D		&	245.533				\\ \hline
\end{tabular}
}
\caption{Average number of generations and solutions per front after 30 runs per configuration, for methods baseline (B), disjoint (D), overlapped (O) and \textcolor{blue}{automatic} overlapped (A), using a chromosome length of 2048 dimensions. Acronyms next to values indicate that there is not significant difference with respect to that method for that value. Equiv-$X$ implies that value is the same as executing $X$, since both configurations would be the same.}
\label{tab:sols2048}
\end{table*}
%
%EXPLANATION OF THE RESULTS
This can be explained comparing the number of non-dominated solutions
of each front and the average number of generations (Table
\ref{tab:sols512} and Table \ref{tab:sols2048}).

With both chromosome
lengths, increasing the number of islands implies more generations
with all the methods (logically, as there are \textcolor{blue}{fewer} individuals in each
island). But also, the SLA methods
approach to the number of generations with the baseline when
increasing the number of islands. However, with $L=2048$ the migration
time is big enough  to not improve the number of generations
with respect to the baseline, even in the lower number of islands, as
it happens with $L=512$. Therefore, more generations do not
necessarily mean improve the solution of the global PF, but focusing on
different elements of the chromosome. As  previously stated, every
island is unaware of the other islands PFs, and they are trying to
optimize their solutions independently.

With respect to the average
number of solutions per front, there is a clear difference 
 with the baseline with $L=512$, where this value is in the most
of the cases, less than a half. The number of non-dominated solutions
also implies a better Spread indicator, where the baseline 
 obtains better (or not significantly different) values in the majority of the compared configurations.

%ZDT1
\begin{figure}[h!tb]
\centering
\includegraphics[width=12cm]{plot_zdt1_512.png}
\caption{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }
\label{fig:plot_zdt1_512}
\end{figure}
%
\begin{figure}[h!tb]
\centering
\includegraphics[width=12cm]{plot_zdt1_2048.png}
\caption{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }
\label{fig:plot_zdt1_2048}
\end{figure}
%
%ZDT2
\begin{figure}[h!tb]
\centering
\includegraphics[width=12cm]{plot_zdt2_512.png}
\caption{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }
\label{fig:plot_zdt2_512}
\end{figure}
%
\begin{figure}[h!tb]
\centering
\includegraphics[width=12cm]{plot_zdt2_2048.png}
\caption{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }
\label{fig:plot_zdt2_2048}
\end{figure}
%
%ZDT3
\begin{figure}[h!tb]
\centering
\includegraphics[width=12cm]{plot_zdt3_512.png}
\caption{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }
\label{fig:plot_zdt3_512}
\end{figure}
%
\begin{figure}[h!tb]
\centering
\includegraphics[width=12cm]{plot_zdt3_2048.png}
\caption{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }
\label{fig:plot_zdt3_2048}
\end{figure}
%
%
%
%ZDT6
\begin{figure}[h!tb]
\centering
\includegraphics[width=12cm]{plot_zdt6_512.png}
\caption{PFs obtained in one arbitrary run for the ZDT6 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }
\label{fig:plot_zdt6_512}
\end{figure}
%
\begin{figure}[h!tb]
\centering
\includegraphics[width=12cm]{plot_zdt6_2048.png}
\caption{PFs obtained in one arbitrary run for the ZDT6 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }
\label{fig:plot_zdt6_2048}
\end{figure}
